Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-01 journal paper/journal_main.tex
A few more edits re formatting.
Restored \\ to the title.
Edit in the title note.

\title{Competing Bandits: 
\\ The Perils of Exploration under Competition
\thanks{This is a merge of two conference papers,
\citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, 
with a unified presentation.}}
% \textit{Competing Bandits: Learning under Competition}, at Innovations in Theoretical Computer Science 2018, and \textit{The Perils of Exploration under Competition: A Computational Modeling Approach}, at ACM Economics and Computation 2019.}}

\author{Guy Aridor
\footnote{Columbia University, Department of Economics. Email: g.aridor@columbia.edu} 
\and
%\rule{0.2in}{0pt}
Yishay Mansour
\footnote{Google and Tel Aviv University, Department of Computer Science. Email: mansour.yishay@gmail.com;} 
\and
%\rule{0.2in}{0pt}   
Aleksandrs Slivkins\footnote{Microsoft Research New York City. Email: slivkins@microsoft.com} 
\and
%\rule{0.2in}{0pt}   
Zhiwei Steven Wu
\footnote{University of Minnesota - Twin Cities, Department of Computer Science. Email: zsw@umn.edu.\newline
The research has been done when Z.S. Wu has been an intern and a postdoc at Microsoft Research NYC.
}}
\date{First version: July 2020}
\maketitle
\begin{abstract}
Most modern firms strive to learn from interactions with consumers, and many engage in \emph{exploration}: making potentially suboptimal choices for the sake of acquiring new information. We initiate a study of the interplay between \emph{exploration} and \emph{competition}—how such firms balance the exploration for learning and the competition for consumers. Here consumers play three distinct roles: they are customers that generate revenue, they are sources of data for learning, and they are self-interested agents which choose among the competing firms.

@@

\newpage
\bibliographystyle{plainnat}
\bibliography{bib-abbrv,bib-ML,refs,bib-bandits,bib-AGT,bib-slivkins, bib-random}

\begin{appendices}

>>>>

\title{Competing Bandits:\\ 
The Perils of Exploration under Competition%
\thanks{This is a merged and final version of two conference papers,
\citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, 
with a unified and streamlined presentation.}}
% \textit{Competing Bandits: Learning under Competition}, at Innovations in Theoretical Computer Science 2018, and \textit{The Perils of Exploration under Competition: A Computational Modeling Approach}, at ACM Economics and Computation 2019.}}

\author{Guy Aridor%
\footnote{Columbia University, Department of Economics. Email: g.aridor@columbia.edu} 
\and
%\rule{0.2in}{0pt}
Yishay Mansour%
\footnote{Google and Tel Aviv University, Department of Computer Science. Email: mansour.yishay@gmail.com;} 
\and
%\rule{0.2in}{0pt}   
Aleksandrs Slivkins%
\footnote{Microsoft Research New York City. Email: slivkins@microsoft.com} 
\and
%\rule{0.2in}{0pt}   
Zhiwei Steven Wu%
\footnote{University of Minnesota - Twin Cities, Department of Computer Science. Email: zsw@umn.edu.\newline
The research has been done when Z.S. Wu has been an intern and a postdoc at Microsoft Research NYC.
}}
\date{First version: July 2020}
\maketitle
\begin{abstract}
Most modern firms strive to learn from interactions with consumers, and many engage in \emph{exploration}: making potentially suboptimal choices for the sake of acquiring new information. We initiate a study of the interplay between \emph{exploration} and \emph{competition}—how such firms balance the exploration for learning and the competition for consumers. Here consumers play three distinct roles: they are customers that generate revenue, they are sources of data for learning, and they are self-interested agents which choose among the competing firms.

@@

\clearpage
%\addcontentsline{toc}{section}{References}
\bibliographystyle{plainnat}
\bibliography{bib-abbrv,bib-ML,refs,bib-bandits,bib-AGT,bib-slivkins, bib-random}

\clearpage
\begin{appendices}
